
\newpage
%\section*{\begin{center} Bibliography \end{center}}
\begin{thebibliography}{15}
\bibitem{S. Yu } 
S. Yu, C. Wang, K. Ren, and W. Lou. 
\textit{The \ Achieving secure, scalable and fine-grained data access control in\ cloud computing}. 
in Proceedings of the IEEE INFOCOM, March 2010, pp. 1-99
 
\bibitem{Kuo et al.} 
Kuo-Hsuan Huang, En-Chi Chang, and Shao-Jui Wang 
\textit{A \ Patient-Centric Access Control Scheme for Personal Health Records in \ the Cloud}.  Fourth International Conference on Networking and Distributed Computing, 2014. 

\bibitem{Dixit } 
Dixit, G. N
\textit{\ Patient Centric Frame Work For Data Access Control Using Key Management In \ Cloud Server}.  International Journal of Engineering, 2 (4), 2013
 
 \bibitem{Chen } 
Chen, Y. Y., Lu, J. C., Jan, J. K.
\textit{\ A secure EHR system based on hybrid clouds}.  Journal of medical systems, 36 (5), 3375 -3384, 2012.

\bibitem{Leng et } 
Leng, C., Yu, H., Wang, J., Huang, J. 
\textit{The \ Securing Personal Health Records in the
Cloud by Enforcing Sticky Policies}. 
in TELKOMNIKA Indonesian Journal of Electrical Engineering, 11 (4), 2200-2208, 2013.

\bibitem{T. S. Chen } 
T. S. Chen, C. H. Liu, T. L. Chen, C. S. Chen, J. G. Bau, and T.C. Lin \textit{\ Secure Dynamic access control scheme of PHR in cloud computing}.  in Journal of Medical Systems, vol. 36, no. 6, pp. 4005–4020, 2012.

\bibitem{J. Pecarina} 
J. Pecarina, S. Pu, and J.-C. Liu. 
\textit{The \ SAPPHIRE: Anonymity for enhanced control and
private collaboration in healthcare clouds}. 
in Proceedings of the 4th IEEE International Conference on Cloud Computing Technology and Science
(CloudCom), 2012, pp. 99–106.

\bibitem{S. Yu } 
S. Yu, C. Wang, K. Ren, and W. Lou. 
\textit{The \ Achieving secure, scalable and fine-grained data access control in\ cloud computing}. 
in Proceedings of the IEEE INFOCOM, March 2010, pp. 1-99

\bibitem{Duc H. Tran  } 
D.H Tran, N. H.-Long, Z. Wei, N. W. Keong 
\textit{The \ Towards security in sharing data on cloud-based social networks}.  in 8th In-ternational Conference on Information, Communications and Signal Processing (ICICS), 2011, pp. 1-5.

\bibitem{S. Yu } 
Ming Li, Shucheng Yu, and Yao Zheng
\textit{The \ Scalable and Secure Sharing of Personal
Health Records in Cloud Computing Using Attribute-Based Encryption}.  in IEEE Transactions on Parallel and Distributed Systems, 24(1), pp. 131-143, 2013.

\bibitem{S. Yu } 
V. Goyal, O. Pandey, A. Sahai, and B. Waters
\textit{ \ Attribute-Based
Encryption for Fine-Grained Access Control of Encrypted Data}. Proc. 13th ACM Conf. Computer and Comm. Security (CCS 06), pp. 89-98, 2006.

\bibitem{S. Yu } 
M. Chase, and S.S.M. Chow
\textit{\ Improving Privacy and Security in Multi-
Authority Attribute-Based Encryption}.in  Proc. ACM Conf. Computer and Comm. Security, pp. 121-130. 2009

\bibitem{S. Hohenberger } 
R. Canetti, and S. Hohenberger 
\textit{\ Chosen-Ciphertext Secure Proxy Re-
Encryption}.  in Proc. 14th ACM Conf. Computer and Comm. Security (CCS 07), pp. 185-194, 2007.

\bibitem{M. Jafari } 
M. Jafari, R. S. Naini, and N. P. Sheppard
\textit{\ A rights manage-ment approach to protection of privacy in a cloud of electronic health records}.  in 11th annual
ACM workshop on Digital rights management, October 2011, pp. 23-30.

\bibitem{Chen Danwei} 
Chen Danwei, Chen Linling, Fan Xiaowei, He Liwen, Pan Su, and Hu
Ruoxiang  \textit{\ Securing Patient-Centric Personal Health Records Sharing System in Cloud Computing”,}.  in China Communications, Supplement No.1, 2014

\end{thebibliography}


